From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/experiments.tex
smoothed sec4, including discussion

\cs{todo: discuss differences between domains}
\gbt{Not sure we'll have space :) }

\gbt{Note: I've rewritten this intro, the previous version with the plan of what is to be covered is commented out in the tex file}

We use \mn to gain insight into the extent to which current models account for object naming.
We do so in three ways: By analyzing the behavior of existing models on entry-level names, by assessing the consequences of fine-tuning models with entry-level name data, and by analyzing the predictions of the models, comparing them to human naming behavior as attested in \mn.
The latter will be done in Section~\ref{sec:analysis}; here we focus on modeling experiments.
\gbt{Maybe this needs to go in the intro or somewhere else. It's important to stress that the modeling experiments are on entry-level only, and the analysis takes into account the other names.}

The modeling experiments adopt the standard single-label object classification approach of Computer Vision, and we will compare prediction of the original \vg name with the entry-level name.
We leave modeling experiments that take into account other possible names of objects for future work.

@@

\begin{small}
\begin{itemize}
\item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}. The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set 1600 object names in \vg. This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
 \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}). 
For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
\end{itemize}
\end{small}

@@

\begin{small}
\begin{itemize}
\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}
\end{small}

@@

\subsection{Results}
\label{sect:exp_results}
\gbt{To do: streamline to make consistent with motivations + expectations laid out in the previous subsection.}

@@

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
\cs{Left as items for the sake of a better overview for now}
\begin{itemize}
	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the VG name (columns VG), despite being trained on VG.  
	Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
	The results therefore indicate that the FRCNN models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
	\item The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
	This confirms what we observed on the FRCNN results. 
	\item In sum, we find that models learn entry-level naming when being trained on ``\arbitrary'' naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning. 
	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
\end{itemize}

@@

%\iffalse
\cs{under construction}
\begin{itemize}
	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
	\item ... 
	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data. 
\end{itemize}
%\fi

>>>>

Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
% found in the verification data in Section \ref{sec:verification}.
%We leave modeling experiments that take into account other possible names of objects for future work.

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}. The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set 1600 object names in \vg. This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
 \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}). 
For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
\end{itemize}

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. The model uses the VGMN vocabulary.  The model is optimized on VG and MN ground truth names respectively.
 \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
\end{itemize}

@@

\subsection{Results}
\label{sect:exp_results}

@@

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}

A pervasive trend in these results is that all models perform better 
at predicting the entry-level name (columns MN) than the VG name (columns VG), regardless of which vocab and which ground-truth they are trained on.  
Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.

 The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low. This confirms what we observed on the FRCNN results. 
In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning. Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

@@

To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon, which involves a lot of variation when names are freely annotated, but also a lot of agreement.
Hence, it is a striking result that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
The next Section elaborates on this point and proposes a more fair assessment of naming quality achieved by the different models.

\iffalse
\cs{under construction}
\begin{itemize}
	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
	\item ... 
	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data. 
\end{itemize}
\fi
